Reasoning about a Capability Machine with Local Capabilities

### 2017-06-14 popl-2018/paper.tex
Fix compilation.

For our purposes, this restriction is unproblematic, since we are only
interested in proving semantic properties (e.g., an assertion will never fail).
However, in other situations, we may be interested in proving more syntactic
properties like the more syntactic properties, that are often considered in
object capability literature like confinement, no authority amplification etc.
Although such properties are typically more restrictive and less easy to use for
reasoning, \cite{Devriese:2016ObjCap} have demonstrated how a logical relation
much like ours can be adapted to also support them, by quantifying the logical
relation over a custom interpretation of effectful computations and the type of
references. We expect their solution can be readily adapted to our setting,
modulo some details (like the fact that we do not just have read-write
capabilities, but also other types).

>>>>

For our purposes, this restriction is unproblematic, since we are only
interested in proving semantic properties (e.g., an assertion will never fail).
However, in other situations, we may be interested in proving more syntactic
properties like the more syntactic properties, that are often considered in
object capability literature like confinement, no authority amplification etc.
Although such properties are typically more restrictive and less easy to use for
reasoning, \citet{Devriese:2016ObjCap} have demonstrated how a logical relation
much like ours can be adapted to also support them, by quantifying the logical
relation over a custom interpretation of effectful computations and the type of
references. We expect their solution can be readily adapted to our setting,
modulo some details (like the fact that we do not just have read-write
capabilities, but also other types).
